---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gatpkg

Written by Thomas Talbot, revised and converted to Markdown by Abigail Stamm

<!-- badges: start -->
<!-- badges: end -->

This package is maintained by the New York State Department of Health’s 
Environmental Health Surveillance (EHS) Section. Its purpose is to run the 
Geographic Aggregation Tool (GAT) in R. 

Health outcome maps with fine geographic resolution can be misleading due to 
random fluctuations in disease rates caused by small numbers. In some cases 
these maps can also inadvertently disclose confidential data. To overcome 
these limitations EHS developed GAT to join neighboring geographic areas 
together until a user defined population and/or number of cases is reached. 
GAT can be used to produce maps for the public at the finest geographic 
resolution practicable.
    
The input object is a polygon shapefile. The shapefile must contain a 
character variable that uniquely identifies areas 
and a numeric variable to sum for aggregation. A series of dialog boxes 
allows the user to select: a variable to uniquely identify areas, one or 
more aggregation variables, optionally, a variable of areas within which 
merging will be preferred (ex. county), the amount (sum) the aggregation 
variable(s) should be aggregated to, and the preferred aggregation method 
- closest, least value, or ratio. The output is a shapefile with before 
and after choropleth maps in R graphics saved to PDF. For output regions, 
most numeric variables will be summed, except variables with the 
following names, which will be averaged instead: x, y, GATx, GATy, lat, 
lon, latitude, longitude, and long. For character variables, the values 
of the last region merged will be used, with three additional variables 
added: Sp_id for R row number and GATx, GATy for geographic centroids as 
determined by the GAT. 

The user must have an input shapefile (*.shp). The shapefile must have the 
geographic boundaries of the areas the user would like to merge, a character 
variable that uniquely identifies these areas, and a numeric variable to merge 
by, such as the number of cases of disease or the population.

GAT outputs a shapefile containing the aggregated regions with 
associated data, which can be used in GIS programs such as ArcGIS, MapInfo and 
QGIS. A KML file can also be produced, which can be displayed in Google Earth 
as well as other Internet-based mapping programs. Last, GAT outputs several 
before and after plots and a log of all selections and processes.

The package includes an embedded map file to use when testing several of the 
package functions. For details, type \code{?albanytown}. 

If you use GAT, we would appreciate if you cite it. Suggestions for improvement 
and bug reports are welcome.

## Disclaimer

This version of GAT is provided as is. 

GAT was written in R-2.9.2 under Windows XP. It was revised and converted to 
a package in R-3.4.3 under Windows 10 using RStudio-1.1.442. The user needs 
minimal R programming experience to run GAT. 

## Installation

**This is a placeholder. We are not live yet.**

You can install the released version of gatpkg from 
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gatpkg")
```

## Running GAT

This is the primary function to run GAT:

```{r example, eval=FALSE}
# not run
library(gatpkg)
# this is the only code that is likely to matter
# to most users
runGATprogram()
```

The package contains over 20 additional functions that are used in the 
function above and could be combined in different ways to create slightly 
modified versions of GAT. If there are specific conditions or options you 
would like to request, or if you have specific recommendations to improve 
GAT, let us know.

