---
title: "GAT Citation Information"
author: "Abigail Stamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GAT Citation Information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Citation and feedback

Suggestions for improvement and bug reports are welcome. Send feedback to [NYSDOH EPHT](mailto:epht@health.ny.gov?subject=[GAT in R]) and include *GAT in R* in the subject line.

If you use any part of the Geographic Aggregation Tool (GAT) package, please cite it. For the suggested citation, type:

```{r}
citation(package = "gatpkg")
```

## Acknowledgements

The conversion of GAT to an R package would not have been possible without the support of the Centers for Disease Control and Prevention (CDC) National Environmental Health Tracking Program (NEPHT) and NYS Department of Health (NYSDOH) Bureau of Environmental and Occupational Epidemiology (BEOE) staff and interns, including:

**Major contributors**  
Abigail Stamm, NYSDOH BEOE  
Gwen (Babcock) LaSelva, NYSDOH BEOE  
Thomas Talbot  

**Alpha testers and contributors**  
Neil Muscatiello, NYSDOH BEOE  
Arjita Rai  
Catherine Wargo, NYSDOH BEOE  
Douglas Done, NYSDOH BEOE  
Maxime Fokoua Dongmo  
Marine Nalbandyan  

**Beta testers**  
Angela Werner, CDC NEPHT  
Aya Abdelfattah  
Anne Pysnik, NYSDOH BEOE

GAT was made possible through funding made available to the New York State Department of Health / Health Research, Incorporated by the CDC through grant # NUE1EH001341-03-01. Its content is solely the responsibility of the authors and does not necessarily represent the official views of the CDC.

