---
title: "Geographic Aggregation Tool (GAT) Setup Instructions"
author: "Abigail Stamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GAT Setup Instructions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing and running GAT


```{r, eval = FALSE, echo=FALSE}
# This is a placeholder. We are not on CRAN yet.
You can install the released version of gatpkg from 
[CRAN](https://CRAN.R-project.org) with `install.packages("gatpkg")`. 
```

The development version of GAT is available on [GitHub](https://github.com/ajstamm/gatpkg).

To load GAT, run `library(gatpkg)`.

To run the entire GAT program with default settings, run `runGATprogram()`. For most users, this function alone is probably sufficient. If you would like more detail on what GAT does, check out the [GAT tutorial](gat_tutorial.html) or the [GAT technical notes](gat_tech_notes.html).

The full default program to run GAT looks like this:

```{r, eval=FALSE}
install.packages("gatpkg")
library(gatpkg)
runGATprogram()
```

The package contains over 30 additional functions, most of which are used in the function `runGATprogram()`. Feel free to use these to customize GAT to meet your needs. 

## Disclaimer

This version of GAT is provided as is. 

GAT was written in R-2.9.2 in Windows XP. It was revised and converted to a package in R-3.4.3 in Windows 10 using RStudio-1.2.5019. It has been tested on R version 3.4.x through R version 4.0.x. The user needs minimal R programming experience to run GAT and basic experience in manipulating R functions for some advanced features. 

