---
title: "GAT for R Setup Instructions"
author: "Abigail Stamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GAT for R Setup Instructions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installing and running GAT

**This is a placeholder. We are not live yet.**

You can install the released version of gatpkg from [CRAN](https://CRAN.R-project.org) with `install.packages("gatpkg")`. 

To load GAT, run `library(gatpkg)`.

To run the entire GAT program as is, run `runGATprogram()`. For most users, this function alone is probably sufficient. If you would like more detail on what this program does, check out the [GAT step by step vignette](gat_basic_manual.html).

The full default program looks like this:

```{r, eval=FALSE}
# not run
install.packages("gatpkg")
library(gatpkg)
runGATprogram()
```

The package contains over 20 additional functions that are used in the function `runGATprogram()`. Feel free to use these to customize GAT to meet your needs. 

# Disclaimer

This version of GAT is provided as is. 

GAT was written in R-2.9.2 under Windows XP. It was revised and converted to a package in R-3.4.3 under Windows 10 using RStudio-1.1.442. The user needs minimal R programming experience to run GAT. 

# Citation and feedback

If you use any part of the GAT package, please cite it. For the suggested citation, type:

```{r}
citation(package = "gatpkg")
```

Suggestions for improvement and bug reports are welcome. Send feedback to epht@health.ny.gov and include *GAT in R* in the subject line.

