---
title: "GAT Setup Instructions"
author: "Abigail Stamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GAT Setup Instructions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing and running GAT

The Geographic Aggregation Tool (GAT) is available from New York State (NYS) Environmental Public Health Tracking (EPHT) [GitHub](https://github.com/NYSTracking/gatpkg).


<!-- # This is a placeholder. We are not on CRAN yet. -->
<!-- You can install the released version of gatpkg from  -->
<!-- [CRAN](https://CRAN.R-project.org) with `install.packages("gatpkg")`.  -->

Until GAT is posted to CRAN, the easiest way to install is from GitHub. You will need to install devtools first. Some users have also reported that they needed to install [RTools](https://cran.r-project.org/bin/windows/Rtools/) first.


```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("NYSTracking/gatpkg", dependencies = TRUE,
                         build_vignettes = TRUE)
```

To load GAT, run `library(gatpkg)`.

To run GAT with default settings, run [runGATprogram()](../html/runGATprogram.html). For most users, this function alone is probably sufficient. If you would like more detail on what GAT does, check out the [GAT tutorial](gat_tutorial.html) or the [GAT technical notes](gat_tech_notes.html).

The full default program to run GAT looks like this:

```{r, eval=FALSE}
# from GitHub
install.packages("devtools")
devtools::install_github("NYSTracking/gatpkg", dependencies = TRUE,
                         build_vignettes = TRUE)
# from CRAN (not yet available)
# install.packages("gatpkg") 
library(gatpkg)
runGATprogram()
```

The package contains over 30 additional functions, most of which are used in the function [runGATprogram()](../html/runGATprogram.html). Feel free to use these to customize GAT to meet your needs. 

## Disclaimer

This version of GAT is provided as is. 

GAT was written in R-2.9.2 in Windows XP. It was revised and converted to a package in R-3.4.3 in Windows 10 using RStudio-1.2.5019. It has been tested on R versions 3.4 through 4.2. The current version runs on R versions 4.0 through 4.2. 

The user needs minimal R programming experience to run GAT and basic experience in manipulating R functions for some advanced features. 

