---
title: "Geographic Aggregation Tool (GAT) Setup Instructions"
author: "Abigail Stamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geographic Aggregation Tool (GAT) Setup Instructions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing and running GAT

**This is a placeholder. We are not live yet.**

You can install the released version of gatpkg from [CRAN](https://CRAN.R-project.org) with `install.packages("gatpkg")`. 

To load GAT, run `library(gatpkg)`.

To run the entire GAT program as is, run `runGATprogram()`. For most users, this function alone is probably sufficient. If you would like more detail on what this program does, check out the [GAT tutorial](gat_tutorial.html).

The full default program looks like this:

```{r, eval=FALSE}
# not run
install.packages("gatpkg")
library(gatpkg)
runGATprogram()
```

The package contains over 20 additional functions that are used in the function `runGATprogram()`. Feel free to use these to customize GAT to meet your needs. 

## Disclaimer

This version of GAT is provided as is. 

GAT was written in R-2.9.2 under Windows XP. It was revised and converted to a package in R-3.4.3 under Windows 10 using RStudio-1.1.442. The user needs minimal R programming experience to run GAT. 

Suggestions for improvement and bug reports are welcome. Send feedback to epht@health.ny.gov and include *GAT in R* in the subject line.

# Citation and feedback

If you use any part of the GAT package, please cite it. For the suggested citation, type:

```{r}
citation(package = "gatpkg")
```

## Acknowledgements

The conversion of GAT to an R package would not have been possible without the support of the Centers for Disease Control and Prevention (CDC) National Environmental Health Tracking Program (NEPHT) and NYS health department staff and interns, including Neil Muscatiello, Arjita Rai, Douglas Done, Catherine Wargo, Christophe Maxime Fokoua Dongmo, Marine Nalbandyan, and others.

This project was funded by the CDC grant NUE1EH001341-03-01. Its content is solely the responsibility of the authors and does not necessarily represent the official views of the CDC.


